\documentclass{article} \usepackage[margin=1in,headheight=57pt,headsep=0.1in]{geometry}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{float}
\usepackage{longtable}
\usepackage{standalone}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{stix} % Use the STIX fonts
\usepackage{hyperref}
\hbadness=99999

% ------------- %
% HEADER/FOOTER %
% ------------- %
\setlength\parindent{0pt}
\setlength\headheight{30pt}
\headsep=0.25in
\lhead{\textbf{tbrpggepp User Manual}}
\rhead{\textbf{12SDD}}


% -------- %
% DOCUMENT %
% -------- %
\begin{document}

% ---------- %
% TITLE PAGE %
% ---------- %
\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1

	\raggedleft % Right align the title page

	\rule{1pt}{\textheight} % Vertical line
	\hspace{0.05\textwidth} % Whitespace between the vertical line and title page text
	\parbox[b]{0.75\textwidth}{ % Paragraph box for holding the title page text, adjust the width to move the title page left or right on the page

		{\Huge\bfseries tbrpggepp User Manual}\\[2\baselineskip] % Title
		{\large\textit{Tutorial and Troubleshooting Guide}}\\[4\baselineskip] % Subtitle or further description
		{\Large\textsc{james denovan}} % Author name, lower case for consistent small caps

		\vspace{0.5\textheight} % Whitespace between the title block and the publisher

		{\noindent Kinross Wolarai School}\\[\baselineskip] % Publisher and logo
	}

\end{titlepage}
\thispagestyle{empty}
\tableofcontents
\pagebreak
\pagestyle{fancy}
\section{Introduction}
tbrpggepp (Text-Based Role-Playing Game Graphical Editor Plus Plus) is a graphical desktop program for creating the narratives of branching text-based computer games. The program works on both Linux and Windows systems, and has two requirements: a working installation of \texttt{Python 3.7} and the Python library \texttt{PyQt5}, which you can install by entering the following command in a terminal: \\

\texttt{pip install PyQt5} \\

Within tbrpggepp, you create the game-world that the player character navigates throughout their quest. You write the words that the player sees, the enemies and scenarios they encounter, and how they navigate your world. You can write a game about anything: from exploring ancient dungeons, to escaping derelict space stations. The only limit is your imagination. \\

To run the program, simply double-click the \texttt{mainMenuForm.py} file and Python should do the rest.
\newpage
\section{Using the Program}
\input{./introFormManual.tex}
\newpage
\input{./mainMenuFormManual.tex}
\newpage
\input{./editTileFormManual.tex}
\newpage
\input{./editItemFormManual.tex}
\newpage
\input{./editEnemyFormManual.tex}
\newpage
\input{./editMovesFormManual.tex}
With all these forms combined, you're all set to start creating text adventure games!
\newpage
\section{Troubleshooting Guide}
\subsection{Issue 1: Invalid world map file!}
\begin{itemize}
	\item This issue is caused simply by not selecting a valid json file. When creating/opening a world-map file, please ensure that the filename ends with "\texttt{.json}".
\end{itemize}
\subsection{Issue 2: No world file selected!}
\begin{itemize}
	\item This issue is caused when one attempts to modify the game-world grid when infact no file has been created or loaded for the Main Menu form. This could have been a result of manually closing the Introduction Form before selecting/creating a file. Please resolve this by using the "file" menu in the top-left of the Main Menu Form to reopen the Introduction form and create/open a valid world-map file.
\end{itemize}
\subsection{Issue 3: Tile name already used!}
\begin{itemize}
	\item Despite the player within the text-game never seeing the given names of tiles, they are essential in that they uniquely define the tile both to the game-designer and the game program internally. Therefore no two tiles can share the same name without overwriting another tile and causing loss of data. \texttt{tbrpggepp} has resolved this temporarily by renaming the newly updated tile with a randomly generated name, which you may rename again to a unique, more human-readable alternative at your leisure.
\end{itemize}
\subsection{Issue 4: Tile name left blank!}
\begin{itemize}
	\item For reasons stated immediately above, the presence of a unique name per each tile is essential to the function of \texttt{tbrpggepp}. Therefore you must enter a unique name into the Edit Tile form before you can save your work.
\end{itemize}
\subsection{Issue 5: The program crashed!}
\begin{itemize}
	\item Whoops! Please tell me what you were doing immediately before the crash and how you were doing it.
\end{itemize}
\end{document}
